### 2021-08-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

@@

\subsection{Cycle Component Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques. Turbines and compressors are analyzed using isentropic efficiencies. Counter flow heat exchangers use the effectiveness-NTU method while black box heat exchangers use a simple energy balance for state point calculations. The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The concentrating solar power cycle is modeled with necessary components including hot and cold TES, reciever, pumps and counter flow heat exchangers.

@@

The modeled cycles have a number of compressors and turbines. The turbines and compressors are modeled for each cycle using constant isentropic efficiency values summarized in Table \ref{tab-cycle-constants}. Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$. The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have a single inlet and outlet. Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component. Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor can be calculated \cite{klein_nellis_2011}.

\subsubsection{Black Box and Counter Flow Heat Exchangers}
%--------------------------------------------------------------------------------------

@@

\begin{equation}
    \label{eq-black}
    \dot{m}_{in}*h_{in} + \dot{Q}_{in} = \dot{m}_{out}*h_{out} + \dot{Q}_{out},
\end{equation}

In this equation the energy input to the system is on the left hand side with $\dot{m}_{in}$ multiplied by $h_{in}$ being energy from the mass flow and $\dot{Q}_{in}$ being heat transfer directly to the flow from an outside source. The right hand side of the equation is heat leaving the energy balance. The mass flow leaving is $\dot{m}_{out}$ with enthalpy of $h_{out}$ and $\dot{Q}_{out}$ is the heat transfer leaving from the flow. Black box energy balances are used in three situations, the Reciever, LFR HX, and PC HX. These heat exchangers are not exchaustively modeled because the state points on the inlet and outlet are constrained by design parameters.

Counter flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side. The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature. A diagram showing a simplified example of a counterflow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simple counter flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

Additional assumptions of the counter flow heat exchanger model are no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, and no pressure drops accross the heat exchangers. Counter flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature. In all of the modeled cases, the approach temperature is set to a value of 10 K. The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.

To analyze the counter flow heat exchanger a side is chosen, usually high, to start the calculations. The approach temperature is initially subtracted from the hot stream on the high side to find the missing cold temperature according to Equation \ref{temp_h}.

@@

Where T$_{out,c}$ is the cold stream outlet temperature and T$_{in,h}$ is the hot stream inlet temperature. Knowing the two state points allows for the enthalpy to be found using correlations from the fluid property libraries.

[More Desctription on Counterflow HX]

@@

\begin{equation}
    \label{eq-lfr-black-box}
    \dot{m}_{inlet}*h_{inlet} + \dot{Q}_{LFRHX} = \dot{m}_{outlet}*h_{outlet},
\end{equation}

Where the left hand side, $\dot{m}_{inlet}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}_{outlet}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transfered into the cycle, $\dot{Q}_{LFRHX}$, is set at 950 MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C. The outlet temperature of the LFR is rigid due to high temperature material limits on the LFR lead side. Low sCO$_2$ LFR inlet temperature has a lower limit of 340$^{\circ}$C and an optimal value of 400$^{\circ}$C. Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.

@@

The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-Salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX). The diagram for this CSP salt cycle is seen in Figure \ref{csp}.

\end{paracol}
%MW: Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. 
\begin{figure}[htb] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/csp.pdf}
    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and csp black box heat input\label{csp}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}. The cold TES temperature takes on three different values according to cycle configuration capabilitites: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C. In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}. The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. It is assumed that only one hot TES charging option can be active at any given time.

The C2S heat exchanger is active during the 'charging' cycle configurations, when the focus is on heat storage for later use. During this process there is no solar salt flow through the receiver. Pump 1 is active moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.

'Non-charging' cycle configurations has the receiver charging the hot TES, C2S heat exchanger is not transfering heat, and the LFR is dispatching energy directly into electrical generation. When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.

\subsection{Generalization of Cycle Modeling}
%======================================================================================

The cycles presented are generalized in order to draw a more direct comparison. The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants. These values are summarized in Table \ref{tab-cycle-constants}.

%MW: Also changing the specialtable position to allow latex to better place tables.
\begin{specialtable}[htbp] 
    \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
    \begin{tabular}{lcc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pump & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 (K)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 (K)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 (K)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 2.88e7 (Pa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3.0e6 (Pa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

In addition to generalized parameters, all cycles have identical recompression sides. The recompression side contains a PreCooler, Low Temperature Recuperator, and two compressors; Main Compressor and ReCompressor.

@@

\begin{specialtable}[H] 
    \caption{Summary of all modeled non-charging and charging cycles with descriptions. \label{tab-cycle_sum}}
    \begin{tabular}{ll}
    \toprule
    \textbf{Cycle Label} & \textbf{Description}\\
    \midrule
    \textit{Non-Charging}\\
    C-LFR-ON & Two-cycle configuration with LFR as heat source.\\
    C-CSP-ON & Two-cycle configuration with CSP as heat source.\\
    C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
    C-2HTR3T-ON & Seperatre CSP and LFR loops each with dedicated HTR and turbine.\\
    \midrule
    \textit{Charging}\\
    C-LFR-PRE & Turbine is prior to the SALT HX.\\
    C-LFR-POST & Turbine is after the SALT HX.\\
    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$. The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.

@@

The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a CSP cycle. This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON. Configuration of components for these two cycles is identical with the exception of heat inputs. C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from the CSP. These two cycles individually operate when the focus of plant operation is primarily electricity generation.

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
    \caption{Diagram for C-LFR-ON with focus on electricity generation\label{c-lfr-on}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency. The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400$^{\circ}$C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint

@@

>>>>

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. Higher efficiencies, in some simple recompression cycles reaching 50\% efficiency, allows for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.  Due to the benefits of sCO$_2$ Brayton cycles the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.

A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day. Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2012, turchi_2013, ho_2015, wang_2018}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch. A LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 595 $^{\circ}$C. LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} . In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.

Implementation of a combined solar and nuclear plant, modeled in a 2020 study from the School of Energy and Power Engineering in Jilin, China, shows a single recompression cycle layout with and emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility with no demonstration of varied cycle arrangements \cite{wang_2020}.

\hl{This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle. Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.}

%Korea Atomic Energy Research Institute \cite{cha_2016}  
%interest in brayton \cite{doe_2012}
%Efficiency 50\% \cite{turchi_2013} \cite{wright_2009}
%Thermal storage \cite{paul_2010} \cite{sioshansi_2010}
%sCO2 Brayton nuclear \cite{dostal_2005} \cite{dostal_2004} \cite{luo_2020}
%sCO2 Brayton solar \cite{turchi_2012} \cite{turchi_2013} \cite{ho_2015} \cite{wang_2018}
%Cycle Configs \cite{turchi_2012} \cite{wang_2018}
%Similar Works \cite{wang_2020}
%Experimental Plants \cite{cha_2016} \cite{wright_2011}

@@

% **************************************

%MW: I've fixed spelling in a few places. You can install a spell checker to highlight misspelled words. I use the "Code spell checker" extension.

\subsection{Cycle Component Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques and are discussed in more detail below. Turbines and compressors are analyzed using isentropic efficiencies. Counter-flow heat exchangers use the effectiveness-NTU method while simplified ``black box'' heat exchangers use a simple energy balance for state point calculations. The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.

@@

Turbines and compressors are modeled for each cycle using constant isentropic efficiency values which are summarized in Table \ref{tab-cycle-constants}. Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$. The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have single inlet and outlet streams. Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor are calculated \cite{klein_nellis_2011}.

%Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.\mw{this is kind of an awkward way to describe what's happening. I think most readers are familiar with isentropic efficiencies and this can be omitted.}

\subsubsection{Black Box and Counter-Flow Heat Exchangers}
%--------------------------------------------------------------------------------------

@@

%\mw{This is for a single flow stream. Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream? Also, the variable should be consistent with the figure, which would be $\dot{Q}_{HX}$. -BW}

\begin{equation}
    \label{eq-black}
    \dot{m} \cdot h_{in} + \dot{Q}_{HX} = \dot{m} \cdot h_{out} ,
\end{equation}

In this equation the energy input to the system is on the left hand side with $\dot{m}$ multiplied by $h_{in}$ being energy from the mass flow while $\dot{Q}_{HX}$ is heat transfer directly into, positive, or out of, negative, the flow from an outside source. The right hand side of the equation is heat leaving the black box heat exchanger with $\dot{m}$ and enthalpy of $h_{out}$. Black box energy balances are used in three situations, the receiver, LFR heat exchanger, and PC heat exchanger. These heat exchangers are not exhaustively modeled because the state points on the inlet and outlet are defined by design parameters.

Counter-flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side. The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature. A diagram showing a simplified counter-flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simple counter-flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

Additional assumptions of the counter-flow heat exchanger model are: no heat loss to the surroundings, no pressure drops across the heat exchangers, and no fouling resistances. In Figure \ref{counter-flow-hx} the subscript 'out' denotes where the streams are leaving, 'in' denotes the entering streams, 'c' and 'h' signify cold and hot streams respectively, $\dot{Q}_{HX}$ is the total heat transfer from the hot to cold stream, and $\dot{Q}_{surr}$ is the heat transfer to the surroundings.

Counter-flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature. \hl{In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers} \cite{seidel_2010_model_development}. 
%\mw{Justify -BW} 
The fluid libraries referenced are built into EES for Carbon Dioxide and Salt (60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.

To analyze the counter-flow heat exchanger a side is chosen, usually the high side, to start the calculations. The approach temperature is initially subtracted from the hot stream on the high temperature side to find the missing cold temperature according to Equation \ref{temp_h}.

@@

Where T$_{out,c}$ is the cold stream outlet temperature and T$_{in,h}$ is the hot stream inlet temperature. Knowing the two state points allows for the enthalpy out to be found using correlations from the fluid property libraries. This enthalpy then allows for the heat transfer of the heat exchanger to be found with Equation \ref{heattrans_h}.

\begin{equation}
    \label{heattrans_h}
     \dot{Q}_{HX} = \dot{m}_{c}(h_{out,c}-h_{in,c}),
 \end{equation}

 Where $\dot{Q}_{HX}$ is the total heat transfer rate from the hot stream to the cold stream, $\dot{m}_{c}$ is the mass flow rate of the cold stream, $h_{out,c}$ is the enthalpy at the outlet of the cold side, and $h_{in,c}$ is the inlet of the cold side.
 The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is done with Equation \ref{enthalpy_h}.

 \begin{equation}
    \label{enthalpy_h}
     h_{out,h} = h_{in,h} - \frac{\dot{Q}_{HX}}{\dot{m}_{h}},
 \end{equation}

Knowing the hot stream enthalpy out allows for all states to be set on the outlets and inlets of the counter-flow heat exchanger. The temperature difference of the low side is then checked to ensure that it is larger than the approach temperature, defined at $10^\circ$C. If the temperature difference on the low side is smaller than the approach temperature, the same computations are carried with the low side as the starting point.

Knowing the state points on all inlets and outlets of the counter-flow heat exchanger allows for the heat exchanger performance metrics to be calculated. Performance metrics include effectiveness, capacitance ratio, UA, and NTU for heat exchangers. Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, or a perfect heat exchanger with no approach temperature. Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_max$ is found with the maximum enthalpy. Maximum enthalpy of the cold stream is found with correlations by setting the temperature to T$_{in,h}$ with same pressure on the cold outlet. Using the maximum enthalpy, $h_{max}$, the maximum heat transfer rate is calculated using Equation \ref{heattrans_max}.

\begin{equation}
    \label{heattrans_max}
    \dot{Q}_{max} = \dot{m}_{c}(h_{max}-h_{in,c}),
\end{equation}

Calculating the maximum heat transfer rate allows for effectiveness to be calculated using the ratio in Equation \ref{effective}.

\begin{equation}
    \label{effective}
    \varepsilon = \frac{\dot{Q}_{HX}}{\dot{Q}_{max}},
\end{equation}

All of the prior equations are carried out in a built in function within EES. EES is an iterative solver, therefore as long as there is a feasible solution, the functions can take any of the four state points around the heat exchanger and converge on a solution.

After the effectiveness is solved for, capacitance ratio is necessary. The capacitance ratio is defined as the average minimum capacitance rate, $\dot{C}_{min}$, over the average maximum capacitance rate, $\dot{C}_{max}$. Average capacitance rates for the hot and cold streams are found by multiplying the addition of the specific heat at the inlet and outlet of the stream by the mass flow and dividing by two as seen in Equation \ref{avg_cap}.

\begin{equation}
    \label{avg_cap}
    \dot{C}_{avg} = \frac{\dot{m}(c_{in}+c_{out})}{2},
\end{equation}

Where $C_{avg}$ is the average capacitance rate across the hot or cold stream and $c_{in}$ and $c_{out}$ is the specific heat at the inlet and outlet respectively. Specific heat is found using library correlations. Once both average capacitances are calculated for the hot and cold streams, the one will have a larger value, $\dot{C}_{max}$, and one will have a smaller value,  $\dot{C}_{min}$. These maximum and minimum values are then used to find the capacitance ratio, $CR$, in Equation \ref{cap_ratio}.

\begin{equation}
    \label{cap_ratio}
    CR = \frac{\dot{C}_{min}}{\dot{C}_{max}},
\end{equation}

\hl{Using values of effectiveness and capacitance ratio, the effectiveness-NTU method can be employed to find the number of transfer units, $NTU$, and the conductance, $UA$} \cite{klein_nellis_2011,nellis_klein_2008}.

@@

\begin{equation}
    \label{eq-lfr-black-box}
    \dot{m} \cdot h_{inlet} + \dot{Q}_{LFRHX} = \dot{m} \cdot h_{outlet},
\end{equation}

%\mw{If mass is conserved, use a single $\dot{m}$ - BW}

Where the left hand side, $\dot{m}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C. 
%\mw{Make sure numbers are in math mode -BW}
The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side. Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by our industry partner.
%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.

@@

The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-salt counter-flow heat exchanger (C2S), and CSP counter-flow heat exchanger (CSP HX). The diagram for this CSP salt cycle is seen in Figure \ref{csp}.

%\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. -BW}

% \end{paracol}

\begin{figure}[H] 
    %[htb]
    \widefigure
    \includegraphics[width=10 cm]{Definitions/csp.pdf}
    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and csp black box heat input\label{csp}}
\end{figure}
% \begin{paracol}{2}
% \linenumbers
% \switchcolumn

The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}. The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C. In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}. The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. While the hot TES is charging the receiver and LFR are storing heat for later use when grid demand increases. The hot TES storage is not dispensing salt for use in the CSP cycle while charging.

\hl{The C2S heat exchanger is active in the 'charging' cycle configurations, when the focus is on heat storage for later use. Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle. Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver then being stored in the hot TES.}
%\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }

'Non-charging' cycle configurations are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity. When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.

\subsection{Standardization of Cycle Modeling}
%======================================================================================
%\mw{What do you mean by ``generalized?''-BW}

In order to draw a more direct comparison, the cycles are standardized in terms of isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants. These values are summarized in Table \ref{tab-cycle-constants}.

\begin{specialtable}[H] 
    %[htbp]
    %\mw{Also changing the specialtable position to allow latex to better place tables.-BW}
    \caption{Standardized constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
    \begin{tabular}{L{0.5\linewidth}cc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pump & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 ($^{\circ}$C)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 ($^{\circ}$C)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 ($^{\circ}$C)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 28.8 (MPa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 950 (MW)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 750 (MW)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 40 ($^{\circ}$C)\\
    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 595 ($^{\circ}$C)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726 (MPa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3 (MPa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

In addition to generalized parameters, all cycles have identical recompression sides. The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor. 
\mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations. It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.}
%\mw{components don't need to be capitalized -- they aren't proper nouns -BW}

@@

\begin{specialtable}[H] 
    \caption{Summary of all modeled non-charging and charging cycles with descriptions. \label{tab-cycle_sum}}
    \begin{tabular}{lL{0.7\linewidth}}
    \toprule
    \textbf{Cycle Label} & \textbf{Description}\\
    \midrule
    \textit{Non-Charging}\\
    C-LFR-ON & Two-cycle configuration with LFR as heat source.\\
    C-CSP-ON & Two-cycle configuration with CSP as heat source.\\
    C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
    C-2HTR3T-ON & Separate CSP and LFR loops each with dedicated HTR and turbine.\\
    \midrule
    \textit{Charging}\\
    C-LFR-PRE & Turbine is prior to the SALT HX.\\
    C-LFR-POST & Turbine is after the SALT HX.\\
    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

The numerator in Equation \ref{eq-eta-cycle} is the alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$. The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.

@@

The two-cycle configuration that is tested has independent sCO$_{2}$ loops that share a common CSP salt cycle. This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON. Configuration of components for these two cycles is identical with the exception of heat inputs. C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from the CSP. These two cycles individually operate when the focus of plant operation is primarily electricity generation.

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}. 
%\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.}

\end{paracol}
\begin{figure}[H] 
    %[!h] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
    \caption{Diagram for C-LFR-ON with focus on electricity generation\label{c-lfr-on}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The constrained study is calculated by setting the LFR inlet temperature to the design value of $400^{\circ}$C, which is a requirement of the LFR primary circuit to maximize power output within material limits. In addition to the constrained studies, unconstrained studies are required to test the penalties that LFR inlet temperature has on efficiency. The unconstrained study is performed by gradually increasing the mass flow to the main compressor through a parametric study while maximizing cycle efficiency. In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post. 
%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}

@@

\subsubsection{Large Tables}
\begin{specialtable}[H] 
    %[htbp]
